The Bug Catalog of the Maven Repository Ecosystem

### 2014-01-19 docs/msr.tex
intro draft ready

A software ecosystem can be seen as a collection of software projects,
which are developed and co-evolve in the same environment~\cite{LL10}.
Components can and be interdependent and have multiple versions.
Examples of such ecosystems, are Python's {\sc p}y{\sc py} (Python Package Index),
Perl's {\sc cpan} (Comprehensive Perl Archive Network), Ruby's RubyGems and the
Maven Central Repository.\footnote{\url{http://mvnrepository.com/}}

@@

>>>>

A software ecosystem can be seen as a collection of software projects,
which are developed and co-evolve in the same environment~\cite{LL10}.
Components can be interdependent and have multiple versions.
Examples of such ecosystems include Python's
{\sc p}y{\sc py}\footnote{\url{http://pypy.org/}}
(Python Package Index), Perl's
{\sc cpan}\footnote{\url{http://www.cpan.org/}}
(Comprehensive Perl Archive Network), Ruby's
RubyGems\footnote{\url{http://rubygems.org/}}
and the Maven Central Repository.\footnote{\url{http://mvnrepository.com/}}

@@

To statically analyze the Maven repository
we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs
and has already been used in research~\cite{AP10,SHP06}.
Specifically, we ran FindBugs on all the project versions of all
the projects that exist in the repository
to identify all bugs contained in it.

In this paper we present: a) the experiment performed to obtain the
collection of the metric results that the FindBugs tool produces and
b) how researchers can actually use the dataset and include it in
their research.
